\section{Related Work}
\label{sec:related work}

The impact of job placement on both systems and applications has been the subject of many studies \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}. We focus on the HPC-centric studies here. Skinner et al.\ identified significant performance variability due to network congestion \cite{dskinner} \TODO{what kind of system?}. Bhatele et al.\ studied the performance variability of a specific application, p3FD, running on different HPC production systems with torus network topologies \cite{abhinav-sc13}. They obtained performance consistency in their application when network resources were allocated compactly and exclusively \TODO{and wide variability otherwise?}. Jokanovic et al. studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}. 

Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks. Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns \cite{hoefler-hpdc14} \TODO{very brief blurb of what they did or what they found}. Jain et al. conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}. Their work is based on an analytical model and synthetic workload. Bhatele et al. used \TODO{coarse-grain?} simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}. \TODO{mention Misbah's dragonfly work, for which our work is based on}.

Our work complements the literature in the following ways. First, our simulations are driven by real application traces intended to be representative of production-scale application patterns. Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did. Third, with the CODES simulation toolkit and related network models \TODO{cite codes, Misbah's dragonfly work}, we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity. We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.
